Extracting all spectra for NEON mapped stems

### 2020-09-09 R/spectral-lib.Rmd

```{r load-libraries, message=FALSE}
library(tidyverse)
library(neonUtilities)
#library(devtools)
#install_github('NEONScience/NEON-geolocation/geoNEON', dependencies=TRUE)
library(geoNEON)
library(sp)
#devtools::install_github('earthlab/neonhs')
library(neonhs)
library(Rtsne)
library(ggthemes)
library(dplyr)
```

@@

```{r get-veg-data}
# VS-NOTE: set output directory within the analysis/data/raw_data path 
out_dir <- here::here("analysis","data","raw_data","spectral-lib")
dir.create(out_dir)
dir.create(file.path(out_dir, 'data'))

zipsByProduct(dpID = "DP1.10098.001",
              savepath = file.path(out_dir, 'data'),
              check.size = FALSE)
stackByTable(file.path(out_dir, "data","filesToStack10098"), folder = TRUE)
```

@@

```{r read-map}
vegmap <- read_csv(file.path(out_dir, "data", "filesToStack10098", "stackedFiles", 
                            "vst_mappingandtagging.csv")) %>%
  filter(!is.na(stemAzimuth), !is.na(pointID))
vegind <- read_csv(file.path(out_dir, "data", "filesToStack10098", "stackedFiles",
                             "vst_apparentindividual.csv"))
```

@@

veg %>%
  filter(individualID == "NEON.PLA.D03.JERC.02221") %>%
  View

@@

write_csv(all_spectra, "all_spectra.csv")
```

```{r plot-spectra}
all_spectra <- read_csv("all_spectra.csv")

p <- all_spectra %>%
  group_by(scientificName) %>%
  mutate(n = n()) %>%
  ggplot(aes(wavelength_nm, ifelse(mask, NA, reflectance), group = individualID)) +
  geom_path(alpha = .2) +
  xlab('Wavelength (nm)') +
  ylab('Reflectance') +
  facet_wrap(~reorder(scientificName, -n), labeller = label_wrap_gen()) +
  theme_minimal()
ggsave("spectra.png", plot = p, width = 15, height = 15)
```

Look at the sample sizes per species

```{r ss}
all_spectra %>%
  distinct(scientificName, spectraID) %>%
  count(scientificName) %>%
  ggplot(aes(x = n, y = reorder(scientificName, -n))) +
  geom_point() +
  ylab("Species") +
  xlab("Number of spectra") +
  theme(axis.text.y = element_text(size = 7)) +
  scale_x_log10()
```

Plot repeat samples of individuals:

```{r check-dups}
all_spectra %>%
  count(individualID) %>%
  arrange(-n) %>%
  top_n(1) %>%
  `[`(1:56, ) %>%
  left_join(all_spectra) %>%
  mutate(reflectance = ifelse(mask, NA, reflectance)) %>%
  ggplot(aes(x = wavelength_nm, y = reflectance, color = factor(year))) +
  geom_line() +
  facet_wrap(~individualID)
```

>>>>

```{r load-libraries, message=FALSE}
library(tidyverse)
library(neonUtilities)
#install.packages('remotes')
#remotes::install_github('NEONScience/NEON-geolocation/geoNEON', dependencies=TRUE)
library(geoNEON)
library(sp)
#remotes::install_github('earthlab/neonhs')
library(neonhs)
library(dplyr)
library(here)
```

@@

```{r get-veg-data}
out_dir <- here::here("analysis","data","raw_data","spectral-lib")
dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)

zipsByProduct(dpID = "DP1.10098.001",
              savepath = out_dir,
              check.size = FALSE)
stackByTable(file.path(out_dir, "filesToStack10098"), folder = TRUE)
```

@@

```{r read-map}
vegmap <- read_csv(file.path(out_dir, "filesToStack10098", "stackedFiles", 
                            "vst_mappingandtagging.csv")) %>%
  filter(!is.na(stemAzimuth), !is.na(pointID))
vegind <- read_csv(file.path(out_dir, "filesToStack10098", "stackedFiles",
                             "vst_apparentindividual.csv"))
```

@@

@@

write_csv(all_spectra, file.path(out_dir, "all_spectra.csv"))
```
